An Adaptive Algorithm Employing Continuous Linear Functionals

### 2019-05-27 AutoAlgorithmLinearFunctionalDataVerF.tex
Updates from Overleaf

\subsection{Input and Output Spaces}  Let $\calF$ be a separable Hilbert space of inputs with orthonormal basis $(u_i)_{i \in \bbN}$, and let $\calG$ be a separable Hilbert space of outputs  with orthonormal basis $(v_i)_{i\in \bbN}$. Based on Parseval's identity  the norms for these two spaces may be expressed as the $\ell^2$-norms of their series coefficients:  
\begin{subequations}\label{probDef}
\begin{gather}
f = \sum_{i\in \bbN} \widehat{f}_i u_i \in \calF, \qquad 
\DHJRnorm[\calF]{f}=\DHJRbignorm[2]{(\widehat{f}_i\big)_{i\in \bbN}}, \\
g = \sum_{i\in \bbN} \widehat{g}_i v_i \in \calG, \qquad \DHJRnorm[\calG]{g}=\DHJRbignorm[2]{(\widehat{g}_i\big)_{i\in \bbN}}.
\end{gather}
Let these two bases be chosen so that the linear solution operator, $S:\calF \to \calG$, satisfies
\begin{gather}
S(u_i) = \lambda_i v_i, \quad i \in \bbN, \qquad S(f) = \sum_{i\in \bbN} \lambda_i \widehat{f}_i v_i, \\
\lambda_1 \ge \lambda_2 \ge \cdots > 0, \quad \lim_{i \to \infty} \lambda_i = 0, \qquad
\DHJRnorm[\calF \to \calG]{S} := \sup_{f \ne 0} \frac{\DHJRnorm[\calG]{S(f)}}{\DHJRnorm[\calF]{f}} = \lambda_1.
\end{gather}
\end{subequations}
This setting includes, for example, the recovery of functions, derivatives, indefinite integrals, and solutions of linear (partial) differential equations.  We focus on cases where the exact solution requires an infinite number of series coefficients, $\widehat{f}_i$, in general.

@@

Our problem is not solvable for the whole Hilbert space, $\calF$, as can be demonstrated by contradiction. For any potential algorithm, we show that there exists some $f \in \calF$, that looks like $0$ to the algorithm, but for which $S(f)$ is far from $S(0) = 0$.   Choose any $A \in \calA(\calF)$ and $\varepsilon > 0$, and let $L_1, \ldots, L_n$ be the linear functionals that are used to compute $A(f,\varepsilon)$. Since the output space, $\calG$, is infinite dimensional and $n$ is finite, there exists some nonzero $f \in \calF$ satisfying that $L_1(f) = \cdots = L_n(f) = 0$ with non-zero $S(f)$. This means that $A(cf,\varepsilon) = A(0,\varepsilon)$ for any real $c$, and both of these have approximation error no greater than $\varepsilon$, i.e.,
\begin{align*}
    \varepsilon &\ge \frac 12 \left[ \DHJRnorm[\calG]{S(cf) - A(cf,\varepsilon)} + \DHJRnorm[\calG]{S(-cf) - A(-cf,\varepsilon)}\right] \\
    & =  \frac 12 \left[ \DHJRnorm[\calG]{cS(f) - A(0,\varepsilon)} + \DHJRnorm[\calG]{-cS(f) - A(0,\varepsilon)}\right] \\
    & \ge  \DHJRnorm[\calG]{cS(f)} = \DHJRabs{c}\DHJRnorm[\calG]{S(f)}  \qquad \text{by the triangle inequality}.
\end{align*}
Since $S(f) \ne 0$, it is impossible for this inequality to hold for all real $c$.  The presumed $A$ does not exist, $\calA(\calF)$ is empty, and our problem is not solvable for $\calF$. However, it is solvable for well-chosen subsets of $\calF$, as is shown in the sections below.

@@

\begin{figure}[ht]
	\centering
	\begin{tabular}{cc}
		\includegraphics[width=5.5cm]{ProgramsImages/Function.eps} &
		\includegraphics[width=5.5cm]{ProgramsImages/FunctionWalshFourierCoeffDecay.eps}
		\\ (a) & (b) \\
		\includegraphics[width =5.5cm]{ProgramsImages/Scaled.eps} &
		\includegraphics[width=5.5cm]{ProgramsImages/ScaledWalshFourierCoeffDecay.eps}
		\\ (c) & (d) \\
		\includegraphics[width=5.5cm]{ProgramsImages/Filtered.eps} &
		\includegraphics[width=5.5cm]{ProgramsImages/FilteredWalshFourierCoeffDecay.eps}
		\\ (e) & (f)
	\end{tabular}
	\caption{(a) The function $f(x)={\rm e}^{-3x}\sin(3\pi x^2)$; (b) The first Fourier coefficients of $f$; (c) The function $f_{\text{big}}=100f$; (d) The first Fourier coefficients of $f_{\text{big}}$; (e) The function $f_{\text{fuzzy}}$ resulting from modifying some of $f$ coefficients; (f) The first Fourier coefficients of $f_{\text{fuzzy}}$. \label{fig:fourier_example}}
\end{figure}

@@

However, we can observe a finite number of partial sums, 
\begin{equation} \label{sumdef}
\sigma_j(f) :
= \DHJRnorm[2]{ \left(\lambda_{i} \widehat{f}_{i} \right)_{i=n_{j-1}+1}^{n_j}}, \qquad j \in \bbN,
\end{equation}
where $\bsn  = (n_0, n_1, \ldots)$ is an unbounded, strictly increasing sequence of non-negative integers.  We define the cone of nice input functions to consist of those functions for which the $\sigma_j(f)$ decay at a given rate with respect to one another:
\begin{align} \label{decayconedef}
\calC &= \left\{ f \in \calF : \sigma_{j+r}(f) \le ab^r \sigma_j (f) \ \ \forall j,r \in \bbN \right\} \\
\nonumber
& = \left\{ f \in \calF : \sigma_j(f) \le \min_{1 \le r < j}ab^r\sigma_{j-r}(f) \ \ \forall j \in \bbN \right\}.
\end{align}
Here, $a$ and $b$ are positive numbers that define the inclusivity of the cone $\calC$ and satisfy
\begin{equation*} \label{abcond}
b <1 < a.
\end{equation*}
The constant $a$ is an inflation factor, and the constant $b$ defines the general rate of decay of the $\sigma_j(f)$ for $f \in \calC$. Because $ab^r$ may be greater than one, we do not require the series coefficients of the solution, $S(f)$, to decay monotonically. However, we expect their partial sums to decay steadily.

@@

@@

\begin{algo}\label{algo2}
Given $a$, $b$, the sequence $\bsn$, the cone $\calC$, the input function $f \in \calC$, and the absolute error tolerance $\varepsilon$, set $j=1$.
\begin{description}
\item[Step 1.] Compute $\sigma_{j}(f)$ as defined in \eqref{sumdef}.
\item[Step 2.] Check whether $j$ is large enough to satisfy the error tolerance, i.e.,
    \begin{equation*}\label{covcrit}
          \sigma_{j}(f) \le \frac{\varepsilon\sqrt{1 - b^2}}{ab} .
    \end{equation*}
    If this is true, then return $\widetilde{A}(f,\varepsilon) = A_{n_{j}}(f)$, where $A_n$ is defined in \eqref{optAdef}, and terminate the algorithm.
\item[Step 3.] Otherwise, increase $j$ by $1$ and return to Step $1$.
\end{description}
\end{algo}

\begin{theorem}\label{thm:compcost}
The algorithm, $\widetilde{A}$, defined in Algorithm \ref{algo2} lies in $\calA(\calC)$ and has computational cost $\textup{cost}(\widetilde{A},f,\varepsilon)=n_{j^*}$, where $j^*$ is defined implicitly by the inequalities 
\begin{equation} \label{eq:OurAlgjstar}
j^* = \min\left \{ j \in \bbN : \sigma_{j}(f) \le \frac{\varepsilon\sqrt{1 - b^2}}{ab}  \right\}.
\end{equation}
Moreover, $\textup{cost}(\widetilde{A},\calC,\varepsilon,\rho) \le n_{j^\dagger}$, where $j^\dagger$ satisfies the following upper bound:
\begin{equation} \label{jdagger}
j^\dagger \le \min \left \{j \in \bbN : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{j-1} \frac{b^{2(k-j)}}{a^2\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}\right]   \right\}.
\end{equation}

\end{theorem}

@@

A rough upper bound on $j^\dagger$ may be obtained by noting that for any $f \in \calC \cap \calB_\rho$ and for any $j < j^* \le j^\dagger$, it follows from \eqref{eq:OurAlgjstar} and \eqref{normsigineq} that 
\begin{equation*}
\rho \ge \DHJRnorm[\calF]{f} \ge \DHJRbignorm[2]{\big( \widehat{f}_i \big)_{i=n_{j-1}+1}^{n_j}} \ge \frac{\sigma_j(f)}{\lambda_{n_{j-1}+1}} > \frac{\varepsilon\sqrt{1 - b^2}}{ab \lambda_{n_{j-1}+1}}
\end{equation*}
Thus, one upper bound on $j^\dagger$ is the smallest $j$ violating the above inequality:
\begin{equation} \label{jdaggerlast}
j^\dagger \le \min \left \{j \in \bbN :  \lambda_{n_{j-1}+1} \le \frac{\varepsilon\sqrt{1 - b^2}}{ab \rho} \right\}.
\end{equation}

The tighter upper bound in Theorem \ref{thm:compcost} may be obtained by a more careful argument in a similar vein.  
For any $f \in  \calC \cap \calB_\rho$ satisfying $n_{j^*} = \textup{cost}(\widetilde{A},f,\varepsilon) = \textup{cost}(\widetilde{A}, \calC, \varepsilon, \rho) = n_{j^{\dagger}}$ and for any $j < j^* = j^\dagger$,
\begin{align*}
\rho^2 &\ge \DHJRnorm[\calF]{f}^2 = \DHJRbignorm[2]{\big( \widehat{f}_i \big)_{i=1}^{\infty}}^2 \\
& \ge \sum_{k=1}^j \DHJRbignorm[2]{\big( \widehat{f}_i \big)_{i=n_{k-1}+1}^{n_k}}^2 \\
& \ge \sum_{k=1}^j \frac{\sigma_k^2(f)}{\lambda_{n_{k-1}+1}^2} \qquad \text{by \eqref{normsigineq}}\\
& \ge \sum_{k=1}^{j-1} \frac{ b^{2(k-j)}\sigma_j^2(f)}{a^{2}\lambda_{n_{k-1}+1}^2} + \frac{\sigma_j^2(f)}{\lambda_{n_{j-1}+1}^2} \qquad \text{by \eqref{decayconedef}} \\
& = \sigma_j^2(f) \left[ \sum_{k=1}^{j-1} \frac{b^{2(k-j)}}{a^{2} \lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}\right].
\end{align*}
Note that the quantity in the square brackets is an increasing function of $j$ because as $j$ increases, the sum includes more terms and $b^{2(k-j)}$ also increases.

So, for any $j < j^* = j^\dagger$ it follows from the termination criterion in \eqref{eq:OurAlgjstar} that
\begin{equation*}
\rho^2 > \frac{\varepsilon^2(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{j-1} \frac{ b^{2(k-j)}}{a^{2}\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}\right].
\end{equation*}
Thus, any $j$ that violates the above inequality, must satisfy $j \ge j^\dagger$, establishing \eqref{jdagger}.
\end{proof}

@@

The upper bound on $\textup{cost}(\widetilde{A},\calC,\rho,\varepsilon)$ in Theorem \ref{thm:compcost}  is a non-decreasing function of $\rho/\varepsilon$, which depends on the behavior of the sequence $(\lambda_{n_j})_{j=0}^\infty$.  This in turn depends both on the increasing sequence $\bsn$ and on the non-increasing sequence $(\lambda_i)_{i=1}^\infty$. Consider the  term enclosed in square brackets on the the right hand side of the inequality in \eqref{jdagger}: \begin{equation*} \label{keysum}
\sum_{k=1}^{j-1} \frac{b^{2(k-j)}}{a^2\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}.
\end{equation*}
One can imagine that in some cases the first term in the sum dominates, while in other cases the term outside the sum dominates, all depending on how $b^{k-j}/\lambda_{n_{k-1}+1}$ behaves with $k$ and $j$.  These simplifications lead to two simpler, but coarser upper bounds on the cost of $\widetilde{A}$.

\begin{corollary} For the algorithm, $\widetilde{A}$, defined in Algorithm \ref{algo2}, we have $\textup{cost}(\widetilde{A},\calC,\varepsilon,\rho) \le n_{j^\dagger}$, where $j^\dagger$ satisfies the following upper bound:
\begin{equation} \label{jdaggerfirst}
j^\dagger \le \left \lceil \log\left(\frac{\rho a^2\lambda_{n_{0}+1} }{\varepsilon \sqrt{1 - b^2}}\right) \middle/ \log\left(\frac{1}{b}\right) \right \rceil.
\end{equation}
Moreover, if the $\lambda_{n_{j-1}+1}$ decay as quickly as
\begin{equation}
\label{lambdankbd}
\lambda_{n_{j-1}+1} \le \alpha \beta^j,  \quad j \in \bbN,  \qquad \text{for some } \alpha > 0, \ 0 < \beta < 1.
\end{equation}
then $j^\dagger$ also satisfies the following upper bound:
\begin{equation}
\label{jdaggerlastsimple}
j^\dagger \le
\left \lceil \log\left(\frac{\rho a\alpha b }{\varepsilon \sqrt{1 - b^2}}\right) \middle/ \log\left(\frac{1}{\beta}\right) \right \rceil.
\end{equation}
\end{corollary}

\begin{proof}
Ignoring all but the first term in the sum in \eqref{jdagger} implies that 
\begin{equation*} \label{jsumupperbd}
j^\dagger \le \min \left \{j \in \bbN : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^2b^2} \frac{b^{2(1-j)}}{a^2\lambda_{n_{0}+1}^2}    \right\}.
\end{equation*}
This implies \eqref{jdaggerfirst}.

Ignoring all but the term outside the sum leads to the simpler upper bound in \eqref{jdaggerlast}.  If the $\lambda_{n_{j-1}+1}$ decay as assumed in \eqref{lambdankbd} then
\[
j^\dagger \le \min \left \{j \in \bbN :  \alpha \beta^j \le \frac{\varepsilon\sqrt{1 - b^2}}{ab \rho} \right\},
\]
which implies \eqref{jdaggerlastsimple}.
\end{proof}

This corollary highlights two limiting factors on the computational cost of our adaptive algorithm, $\widetilde{A}$. When $j$ is large enough to make $\lambda_{n_{j-1}+1}\DHJRnorm[\calF]{f}/\varepsilon$ small enough, $\widetilde{A}(f,\varepsilon)$ stops.  This is statement \eqref{jdaggerlastsimple}, and its precursor, \eqref{jdaggerlast}.  Alternatively, the assumption that the $\sigma_j(f)$ are steadily decreasing, as specified in the definition of $\calC$ in \eqref{decayconedef}, means that $\widetilde{A}(f,\varepsilon)$ also must stop by the time $j$ becomes large enough with respect to $\lambda_{n_0+1}\DHJRnorm[\calF]{f}/\varepsilon$.

@@

\begin{corollary} \label{cor:tAsameCosthA} Suppose that the sequence $\bsn$ is chosen to satisfy
\begin{equation} \label{lambdaDecay}
\lambda_{n_{j+1}+1} \ge c_\lambda \lambda_{n_j+1}, \qquad j \in \bbN, 
\end{equation}
for some positive $c_\lambda$.  Then $\textup{cost}(\widetilde{A},\calC, \varepsilon,\rho)$ is essentially no worse than \linebreak[4]
$\textup{cost}(\widehat{A},\calB_{\rho},\varepsilon)$ in the sense of \eqref{essNoWorseDef}. 
\end{corollary}

>>>>

\subsection{Input and Output Spaces}  Let $\calF$ be a separable Hilbert space of inputs with orthonormal basis $(u_i)_{i \in \bbN}$, and let $\calG$ be a separable Hilbert space of outputs  with orthonormal basis $(v_i)_{i\in \bbN}$. Based on Parseval's identity  the norms for these two spaces may be expressed as the $\ell^2$-norms of their series coefficients:  
\begin{subequations}\label{probDef}
\begin{gather}
f = \sum_{i\in \bbN} \widehat{f}_i u_i \in \calF, \qquad 
\DHJRnorm[\calF]{f}=\DHJRbignorm[2]{(\widehat{f}_i\big)_{i\in \bbN}}, \\
g = \sum_{i\in \bbN} \widehat{g}_i v_i \in \calG, \qquad \DHJRnorm[\calG]{g}=\DHJRbignorm[2]{(\widehat{g}_i\big)_{i\in \bbN}}.
\end{gather}
Let these two bases be chosen so that the linear solution operator, $S:\calF \to \calG$, satisfies
\begin{gather}
S(u_i) = \lambda_i v_i, \quad i \in \bbN, \qquad S(f) = \sum_{i\in \bbN} \lambda_i \widehat{f}_i v_i, \\
\lambda_1 \ge \lambda_2 \ge \cdots > 0, \quad \lim_{i \to \infty} \lambda_i = 0, \qquad
\DHJRnorm[\calF \to \calG]{S} := \sup_{f \ne 0} \frac{\DHJRnorm[\calG]{S(f)}}{\DHJRnorm[\calF]{f}} = \lambda_1.
\end{gather}
\end{subequations}
This setting includes, for example, the recovery of functions, derivatives, indefinite integrals, and solutions of linear (partial) differential equations.  We focus on cases where the exact solution requires an infinite number of series coefficients, $\widehat{f}_i$, in general, i.e., all $\lambda_i$ are positive.

@@

Our problem is not solvable for the whole Hilbert space, $\calF$, as can be demonstrated by contradiction. For any potential algorithm, we show that there exists some $f \in \calF$, that looks like $0$ to the algorithm, but for which $S(f)$ is far from $S(0) = 0$.   Choose any $A \in \calA(\calF)$ and $\varepsilon > 0$, and let $L_1, \ldots, L_n$ be the linear functionals that are used to compute $A(0,\varepsilon)$. Since the output space, $\calG$, is infinite dimensional and $n$ is finite, there exists some nonzero $f \in \calF$ satisfying that $L_1(f) = \cdots = L_n(f) = 0$ with non-zero $S(f)$. This means that $A(cf,\varepsilon) = A(0,\varepsilon)$ for any real $c$, and both of these have approximation error no greater than $\varepsilon$, i.e.,
\begin{align*}
    \varepsilon &\ge \frac 12 \left[ \DHJRnorm[\calG]{S(cf) - A(cf,\varepsilon)} + \DHJRnorm[\calG]{S(-cf) - A(-cf,\varepsilon)}\right] \\
    & =  \frac 12 \left[ \DHJRnorm[\calG]{cS(f) - A(0,\varepsilon)} + \DHJRnorm[\calG]{-cS(f) - A(0,\varepsilon)}\right] \\
    & \ge  \DHJRnorm[\calG]{cS(f)} = \DHJRabs{c}\DHJRnorm[\calG]{S(f)}  \qquad \text{by the triangle inequality}.
\end{align*}
Since $S(f) \ne 0$, it is impossible for this inequality to hold for all real $c$.  The presumed $A$ does not exist, $\calA(\calF)$ is empty, and our problem is not solvable for $\calF$. However, it is solvable for well-chosen subsets of $\calF$, as is shown in the sections below.

@@

@@

However, we can observe a finite number of partial sums, 
\begin{equation} \label{sumdef}
\sigma_j(f) :
= \DHJRnorm[2]{ \left(\lambda_{i} \widehat{f}_{i} \right)_{i=n_{j-1}+1}^{n_j}}, \qquad j \in \bbN,
\end{equation}
where $\bsn  = (n_0, n_1, \ldots)$ is an unbounded, strictly increasing sequence of non-negative integers.  We define the cone of nice input functions to consist of those functions for which the $\sigma_j(f)$ decay at a given rate with respect to one another:
\begin{align} \label{decayconedef}
\calC = \calC_{\bsn,a,b} &= \left\{ f \in \calF : \sigma_{j+r}(f) \le ab^r \sigma_j (f) \ \ \forall j,r \in \bbN \right\} \\
\nonumber
& = \Bigl\{ f \in \calF : \sigma_j(f) \le \min_{1 \le r < j}ab^r\sigma_{j-r}(f) \ \ \forall j \in \bbN \Bigr\}.
\end{align}
Here, $a$ and $b$ are positive numbers that define the inclusivity of the cone $\calC$ and satisfy
\begin{equation*} \label{abcond}
b <1 < a.
\end{equation*}
The constant $a$ is an inflation factor, and the constant $b$ defines the general rate of decay of the $\sigma_j(f)$ for $f \in \calC$. Because $ab^r$ may be greater than one, we do not require the series coefficients of the solution, $S(f)$, to decay monotonically. However, we expect their partial sums to decay steadily.

@@

\frednote{We need some horizontal axis labels for figures (d)--(f).} Figure \ref{fig:fourier_example} shows three functions and their coefficients for the case of Example \ref{exam:exam1} when $r=1$ and $n_j=2^j$. There are three functions: $f(x)={\rm e}^{-3x}\sin(3\pi x^2)$, $f_{\text{big}}=100f$ and $f_{\text{fuzzy}}$. The function $f_{\text{fuzzy}}$ is obtained by taking $\sigma_8(f_{\text{fuzzy}})=250\sigma_8(f)$ and $\sigma_j(f_{\text{fuzzy}})=\sigma_j(f)$ for $j \ne 8$.  Both $f$ and $f_{\text{big}}$ lie in the same cones, $\calC_{\bsn,a,b}$, and both appear similarly nice.  Therefore, we expect adaptive algorithms that are successful for $f$ to also be successful for $f_{\text{big}}$. However, $f_{\text{big}}$ does not lie in some of the balls,  $\calB_{\rho}$, that $f$ lies in.  On the other hand, the high frequency noise in $f_{\text{fuzzy}}$ suggests that only more robust and costly adaptive algorithms would be able to succeed for such an input.  This corresponds to the fact that $f_{\text{fuzzy}}$ does not lie in all cones, $\calC_{\bsn,a,b}$, that $f$ lies in.

\begin{figure}[ht]
\newcommand{\figwidth}{3.5cm}
	\centering
	\begin{tabular}{c@{\quad}c@{\quad}c}
		\includegraphics[width=\figwidth]{ProgramsImages/Function.eps} &
		\includegraphics[width=\figwidth]{ProgramsImages/Scaled.eps} &
		\includegraphics[width=\figwidth]{ProgramsImages/Filtered.eps}
		\\ (a) & (b) & (c) \\
		\includegraphics[width=\figwidth]{ProgramsImages/FunctionWalshFourierCoeffDecay.eps} &
		\includegraphics[width=\figwidth]{ProgramsImages/ScaledWalshFourierCoeffDecay.eps} &
		\includegraphics[width=\figwidth]{ProgramsImages/FilteredWalshFourierCoeffDecay.eps}
		\\ (d) & (e) & (f)
	\end{tabular}
	\caption{(a) The function $f(x)={\rm e}^{-3x}\sin(3\pi x^2)$; (b) The function $f_{\text{big}}=100f$; (c) The function $f_{\text{fuzzy}}$ which results from modifying some of $f$ coefficients, in dark green; (d) The first Fourier coefficients of $f$; (e) The first Fourier coefficients of $f_{\text{big}}$; (f) The first Fourier coefficients of $f_{\text{fuzzy}}$. \label{fig:fourier_example}}
\end{figure}

@@

\begin{algo}\label{algo2}
Given $a$, $b$, the sequence $\bsn$, the cone $\calC$, the input function $f \in \calC$, and the absolute error tolerance $\varepsilon$, set $j=1$.
\begin{description}
\item[Step 1.] Compute $\sigma_{j}(f)$ as defined in \eqref{sumdef}.
\item[Step 2.] Check whether $j$ is large enough to satisfy the error tolerance, i.e.,
    \begin{equation*}\label{covcrit}
          \sigma_{j}(f) \le \frac{\varepsilon\sqrt{1 - b^2}}{ab} .
    \end{equation*}
    If this is true, then return $\widetilde{A}(f,\varepsilon) = A_{n_{j}}(f)$, where $A_n$ is defined in \eqref{optAdef}, and terminate the algorithm.
\item[Step 3.] Otherwise, increase $j$ by $1$ and return to Step $1$.
\end{description}
\end{algo}
\yuhannote{Please check the result of Theorem 1} \frednote{Yuhan, please put $\rho$ and $\varepsilon$ on left.}\yuhannote{Done. Please double check}
\begin{theorem}\label{thm:compcost}
The algorithm, $\widetilde{A}$, defined in Algorithm \ref{algo2} lies in $\calA(\calC)$ and has computational cost $\textup{cost}(\widetilde{A},f,\varepsilon)=n_{j^*}$, where $j^*$ is defined implicitly by the inequalities 
\begin{equation} \label{eq:OurAlgjstar}
j^* = \min\left \{ j \in \bbN : \sigma_{j}(f) \le \frac{\varepsilon\sqrt{1 - b^2}}{ab}  \right\}.
\end{equation}
Moreover, $\textup{cost}(\widetilde{A},\calC,\varepsilon,\rho) \frednote{=} n_{j^\dagger}$, where $j^\dagger$ satisfies the following upper bound:
\begin{equation} \label{jdagger}
j^\dagger \le \min \left \{j \in \bbN : F(j) \ge \frac{\rho^2 a^4}{\varepsilon^2(1 - b^2)} \right\},
\end{equation}
% \begin{equation} \label{jdagger}
% j^\dagger \le \min \left \{j \in \bbN : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^4} F(j) \right\},
% \end{equation}
where $F$ is the strictly increasing function defined as
\begin{equation} \label{jsum}
F(j): = \sum_{k=0}^{j-1} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}, \qquad j \in \N.
\end{equation}
\end{theorem}

@@

A rough upper bound on $j^\dagger$ may be obtained by noting that for any $f \in \calC \cap \calB_\rho$ and for any $j < j^* \le j^\dagger$, it follows from \eqref{eq:OurAlgjstar} and \eqref{normsigineq} that 
\begin{equation*}
\rho \ge \DHJRnorm[\calF]{f} \ge \DHJRbignorm[2]{\big( \widehat{f}_i \big)_{i=n_{j-1}+1}^{n_j}} \ge \frac{\sigma_j(f)}{\lambda_{n_{j-1}+1}} > \frac{\varepsilon\sqrt{1 - b^2}}{ab \lambda_{n_{j-1}+1}}
\ge \frac{\varepsilon\sqrt{1 - b^2}}{ab \lambda_{n_{j-1}}}
\end{equation*}
Thus, one upper bound on $j^\dagger$ is the smallest $j$ violating the above inequality:
\begin{equation} \label{jdaggerlast}
j^\dagger \le \min \left \{j \in \bbN :  \lambda_{n_{j-1}} \le \frac{\varepsilon\sqrt{1 - b^2}}{\rho ab } \right\}.
\end{equation}

The tighter upper bound in Theorem \ref{thm:compcost} may be obtained by a more careful argument in a similar vein.  
For any $f \in  \calC \cap \calB_\rho$ satisfying $n_{j^*} = \textup{cost}(\widetilde{A},f,\varepsilon) = \textup{cost}(\widetilde{A}, \calC, \varepsilon, \rho) = n_{j^{\dagger}}$ and for any $j < j^* = j^\dagger$,
\yuhannote{new proof starts here}\frednote{Looks good to me}
\begin{align*}
\rho^2 &\ge \DHJRnorm[\calF]{f}^2 = \DHJRbignorm[2]{\big( \widehat{f}_i \big)_{i=1}^{\infty}}^2  \ge \sum_{k=1}^j \DHJRbignorm[2]{\big( \widehat{f}_i \big)_{i=n_{k-1}+1}^{n_k}}^2 \\
& \ge \sum_{k=1}^j \frac{\sigma_k^2(f)}{\lambda_{n_{k-1}+1}^2} \qquad \text{by \eqref{normsigineq}}\\
& \ge \sum_{k=1}^{j-1} \frac{ b^{2(k-j)}\sigma_j^2(f)}{a^{2}\lambda_{n_{k-1}+1}^2} + \frac{\sigma_j^2(f)}{\lambda_{n_{j-1}+1}^2} \qquad \text{by \eqref{decayconedef}} \\
& = \sigma_j^2(f) \left[ \sum_{k=1}^{j-1} \frac{b^{2(k-j)}}{a^{2} \lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{j-1}+1}^2}\right]\\
&> \frac{ \sigma_j^2(f)}{a^2} \sum_{k=1}^{j} \frac{b^{2(k-j)}}{\lambda_{n_{k-1}+1}^2}  \qquad \text{since } a > 1\\
&= \frac{ \sigma_j^2(f)}{a^2}\sum_{k=0}^{j-1} \frac{b^{2(k+1-j)}}{\lambda_{n_{k}+1}^2}  \\
& \ge  \frac{b^2 \sigma_j^2(f)}{a^2} \sum_{k=0}^{j-1} \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}  \qquad \text{since } \lambda_{n_k} \ge \lambda_{n_k+1}\\
& = \frac{b^2 \sigma_j^2(f)}{a^2} F(j)
\qquad \text{by } \eqref{jsum}.
\end{align*}

So, for any $j < j^* = j^\dagger$ it follows from the termination criterion in \eqref{eq:OurAlgjstar} that
\begin{equation*}
 F(j) < \frac{ \rho^2 a^4}{\varepsilon^2(1 - b^2)}.
\end{equation*}
Note from \eqref{jsum} that $F$ is an increasing function because as $j$ increases, the sum defining $F$ includes more positive terms and $b^{2(k-j)}$ also increases. Thus, any $j$ that violates the above inequality, must satisfy $j \ge j^\dagger$.  This establishes \eqref{jdagger}.
\end{proof}

@@

\yuhannote{Also change the analysis and corollary 1}
The upper bound on $\textup{cost}(\widetilde{A},\calC,\rho,\varepsilon)$ in Theorem \ref{thm:compcost}  is a non-decreasing function of $\rho/\varepsilon$, which depends on the behavior of the sequence $(\lambda_{n_j})_{j=0}^\infty$.  This in turn depends both on the increasing sequence $\bsn$ and on the non-increasing sequence $(\lambda_i)_{i=1}^\infty$. Considering the sum $F(j)$,
one can imagine that in some cases the first term in the sum $F(j)$ dominates, while in other cases the last term in the sum dominates, all depending on how $b^{k-j}/\lambda_{n_{k}}$ behaves with $k$ and $j$.  These simplifications lead to two simpler, but coarser upper bounds on the cost of $\widetilde{A}$.

\begin{corollary} For the algorithm, $\widetilde{A}$, defined in Algorithm \ref{algo2}, we have $\textup{cost}(\widetilde{A},\calC,\varepsilon,\rho) \le n_{j^\dagger}$, where $j^\dagger$ satisfies the following upper bound:
\begin{equation} \label{jdaggerfirst}
j^\dagger \le \left \lceil \log\left(\frac{\rho a^2\lambda_{n_{0}} }{\varepsilon \sqrt{1 - b^2}}\right) \middle/ \log\left(\frac{1}{b}\right) \right \rceil.
\end{equation}
Moreover, if the $\lambda_{n_{j-1}}$ decay as quickly as
\begin{equation}
\label{lambdankbd}
\lambda_{n_{j-1}} \le \alpha \beta^j,  \quad j \in \bbN,  \qquad \text{for some } \alpha > 0, \ 0 < \beta < 1.
\end{equation}
then $j^\dagger$ also satisfies the following upper bound:
\begin{equation}
\label{jdaggerlastsimple}
j^\dagger \le
\left \lceil \log\left(\frac{\rho a^2\alpha b }{\varepsilon \sqrt{1 - b^2}}\right) \middle/ \log\left(\frac{1}{\beta}\right) \right \rceil.
\end{equation}
\end{corollary}

\begin{proof}
Ignoring all but the first term in the definition of $F$ in \eqref{jsum} implies that 
\begin{equation*} \label{jsumupperbd}
j^\dagger \le \min \left \{j \in \bbN : b^{-2j}  \ge  \frac{\rho^2 a^4 \lambda_{n_{0}}^2 }{\varepsilon^2(1 - b^2)} \right\}.
\end{equation*}
This implies \eqref{jdaggerfirst}.

Ignoring all but the last term of the sum \eqref{jsum}. leads to the simpler upper bound similar to  \eqref{jdaggerlast}
\begin{equation*} 
j^\dagger \le \min \left \{j \in \bbN :  \lambda_{n_{j-1}}^{-1} \ge \frac{ \rho a^2b}{ \varepsilon\sqrt{1 - b^2}} \right\}.
\end{equation*}
If the $\lambda_{n_{j-1}}$ decay as assumed in \eqref{lambdankbd} then
\[
j^\dagger \le \min \left \{j \in \bbN :  \alpha \beta^{-j} \le \frac{\rho a^2b }{ \varepsilon\sqrt{1 - b^2}} \right\},
\]
which implies \eqref{jdaggerlastsimple}.
\end{proof}

This corollary highlights two limiting factors on the computational cost of our adaptive algorithm, $\widetilde{A}$. When $j$ is large enough to make $\lambda_{n_{j-1}}\DHJRnorm[\calF]{f}/\varepsilon$ small enough, $\widetilde{A}(f,\varepsilon)$ stops.  This is statement \eqref{jdaggerlastsimple} 
and its precursor, \eqref{jdaggerlast}.  Alternatively, the assumption that the $\sigma_j(f)$ are steadily decreasing, as specified in the definition of $\calC$ in \eqref{decayconedef}, means that $\widetilde{A}(f,\varepsilon)$ also must stop by the time $j$ becomes large enough with respect to $\lambda_{n_0}\DHJRnorm[\calF]{f}/\varepsilon$.

@@

\yuhannote{corollary 2 is not changed} \frednote{I think we need a small change}
\begin{corollary} \label{cor:tAsameCosthA} Suppose that the sequence $\bsn$ is chosen to satisfy
\begin{equation} \label{lambdaDecay}
\lambda_{n_{j+1}} \ge c_\lambda \lambda_{n_j}, \qquad j \in \bbN, 
\end{equation}
for some positive $c_\lambda$.  Then $\textup{cost}(\widetilde{A},\calC, \varepsilon,\rho)$ is essentially no worse than \linebreak[4]
$\textup{cost}(\widehat{A},\calB_{\rho},\varepsilon)$ in the sense of \eqref{essNoWorseDef}. 
\end{corollary}
